Interspecies comparisons of Mg/Ca ratios in limpet shells

### 2024-06-23 Manuscript.qmd
added temp data again

The analysed specimens, their origin and studies with background information can be found in Table 1.

@@

| Modern         | [@Nicastro2020-ih] | *N. deaureata*   | Bahía Cambaceres Exterior - Tierra del Fuego (AR) | ND-1016-3     | Stable oxygen and carbon isotope analysis                   |

@@

|                | This study         | *N. magellanica* | Heshkaia 35                                       | Heshkaia_35-1 | *none*                                                      |

@@

>>>>

The analysed specimens, their origin and respective studies with research background information can be found in Table 1. Here we will briefly summarise their contextual information, which can be accessed in more detail at the respective studies [@Nicastro2020-ih; @Surge2012-ba; @Graniero2017-io]. While those studies also included other specimens, their accessibility or state of preservation did not all lend them to be re-analysed.

There are two main locations that we sourced specimens from: the island of West Ray in Orkney (UK) and the Beagle Channel in Tierra del Fuego (Argentina). A modern shell on West Ray was collected in Rack Wick Bay in August 2009, which experiences virtually no freshwater input. The temperature

@@

| Modern         | [@Nicastro2020-ih] | *N. deaureata*   | Cambaceres Bay - Tierra del Fuego (AR)          | ND-1016-3     | Stable oxygen and carbon isotope analysis                   |

@@

|                | This study         | *N. magellanica* | Heshkaia 35 in Moat Bay - Tierra del Fuego (AR) | Heshkaia_35-1 | *none*                                                      |

@@

```{r SST Data}
#| fig-cap: SST values averaged over the last 20 years. 
#| fig-height: 10
#| fig-width: 10

# Read the CSV files, skipping the comments
df1 <- read_csv(here("data","Westray-SST.csv"), comment = "#")
df2 <- read_csv(here("data","Tierra_del_Fuego-SST.csv"), comment = "#")

# Combine the datasets with new names and add year and month columns
combined_df <- bind_rows(df1 %>% mutate(dataset = "Westray"),
                         df2 %>% mutate(dataset = "Tierra del Fuego")) %>%
  mutate(analysed_sst = analysed_sst - 273.15,
         time = as_datetime(time),
         year = year(time),
         month = month(time, label = TRUE)) %>%
  group_by(dataset, year, month) %>%
  summarise(mean_sst = mean(analysed_sst, na.rm = TRUE),
            sd_sst = sd(mean_sst, na.rm = TRUE))

# Plot the data
combined_df %>% 
    group_by(dataset, month) %>%
  summarise(sd_sst = sd(mean_sst, na.rm = TRUE),
            mean_sst = mean(mean_sst, na.rm = TRUE)) %>%
ggplot(aes(x = month, y = mean_sst, colour = dataset,group=dataset)) +
  geom_ribbon(aes(ymin = mean_sst - sd_sst, ymax = mean_sst + sd_sst,fill=dataset), alpha = 0.2,col="white") +
  geom_path() +
  scale_colour_manual(values = c( "#007f7f", "#EC7063")) +
scale_fill_manual(values = c( "#007f7f", "#EC7063"))+
  labs(title = "Monthly Sea Surface Temperature",
       x = "Year-Month",
       y = "Mean Analysed SST (°C)") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1),
    legend.position = c(0.1, 0.9))+  
  scale_y_continuous(breaks = c(5, 10, 15),limits = c(3,15)) +
  labs(colour="",fill="")
